---
title: "tsCogs: a time-series cognostic/feature generation and modeling package"
author: "Joseph Clark & Trenton Pulsipher"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{tsCogs: a time-series cognostic/feature generation and modeling package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package was built to take raw data and identify entities which are at risk of negatively changing their behavior. The steps and details involved include:

- create a time-series profile from raw transactional data,    
- determine "truth" via k-means clustering on the shape (normalized) of the time-series profiles,    
- flexibly limit both start and end of the time-series profile for modeling purposes,    
- create generic feature set related to the time-series profiles,    
- apply a machine learning algorithm to model/predict risk of behavior change,    
- pass along details and attributes for each entity not used in each stage list above but useful in driver analysis and other post-prediction efforts.    


## Time-series Profile Creation

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.


## k-means Clustering



## Cut-Point Algorithm

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold', fig.cap = 'figure caption'}
plot(1:10)
plot(10:1)
```


## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
